Fifteen years of decentralization attempts

### 2014-03-24 paper.tex
fixed minor issues

		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority. The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

@@

	\subsection{Other decentralized systems}
		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity. An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible. The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms. Users are able to send and receive unicast, multicast and anycast messages anonymously. The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages. A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.

@@

	\begin{itemize}
		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
		\item{Public implementation:} For each network we will explain whether a public implementation is available.
		\item{Used in practice:} Is the network used in practice?
		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\item{Anonymity:} Does the network hide the identities of the sender and/or receiver?
	\end{itemize}

>>>>

		Instead of the Directory Servers, it uses a DHT and a new Neighbourhood Authority (NA). The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

@@

	\subsection{Anonymizing Peer-to-Peer Proxy}
		Anothe proposed decentralized, anonymizing overlay network is Anonymizing Peer-to-Peer Proxy (AP3) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible. The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms. Users are able to send and receive unicast, multicast and anycast messages anonymously. The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages. A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.

@@

	\begin{itemize}
		\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
		\item{Public implementation:} For each network we will explain whether a public implementation is available.
		\item{Used in practice:} Is the network used in practice?
		\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\item{Unlinkability:} Does the network hide the identities of the sender and/or receiver?
	\end{itemize}
